NumPy---Array Programming in Python

### 2020-01-28 body.tex
Minor edits

SciPy and Matplotlib are tightly coupled with NumPy---in terms of
history, development, and usage.
% to expand the suite of standard algorithms and
% provide basic plotting capabilities.
SciPy provides fundamental algorithms for scientific computing
including mathematical, scientific, and engineering routines.
Matplotlib generates publication-ready figures and visualizations.
The combination of NumPy, SciPy, and Matplotlib together with
an advanced interactive environment like IPython \cite{perez2007ipython}
or Jupyter \cite{Kluyver:2016aa}
provides a complete foundation for array-based scientific computing.
The scientific Python ecosystem (Fig.~\ref{fig:ecosystem}) builds on top of
this foundation to provide several, widely used \emph{technique-specific}
libraries\cite{pedregosa2011scikit,vanderwalt2014scikit,SciPyProceedings_11},
that in turn underlay numerous \emph{domain-specific} projects
\cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,2018EGUGA..2012146H}.
NumPy, as the focal point for the ecosystem of array-aware libraries,
sets documentation standards, provides array testing infrastracture,
and defines minimum version depedencies.

@@

Similar examples can be found in physics, earth sciences, biology,
and more.
Researchers in these fields depend on NumPy being correct, reliable,
and repeatable.
The rich ecosystem of tools building on NumPy and the larger community
of scientists and programmers using those tools mean that NumPy has a
responsibility to maintain considerable stability.
At times, this conflicts with the need to innovate;
resolving it requires balancing trade-offs.
% our focus is ...
% NumPy purpose engages with this problem by ...
% [this also defines the scope of NumPy]
This need creates interesting challenges for NumPy development as the
computational environment scientists are analyzing their data on continues
to evolve and change.
% this leads to a proliferation of arrays

>>>>

SciPy and Matplotlib are tightly coupled with NumPy---in terms of
history, development, and use.
% to expand the suite of standard algorithms and
% provide basic plotting capabilities.
SciPy provides fundamental algorithms for scientific computing
including mathematical, scientific, and engineering routines.
Matplotlib generates publication-ready figures and visualizations.
The combination of NumPy, SciPy, and Matplotlib together with
an advanced interactive environment like IPython \cite{perez2007ipython}
or Jupyter \cite{Kluyver:2016aa}
provides a complete foundation for array-based scientific computing.
The scientific Python ecosystem (Fig.~\ref{fig:ecosystem}) builds on top of
this foundation to provide several, widely used \emph{technique-specific}
libraries\cite{pedregosa2011scikit,vanderwalt2014scikit,SciPyProceedings_11},
that in turn underlay numerous \emph{domain-specific} projects
\cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,sunpy2015,2018EGUGA..2012146H}.
NumPy, as the focal point for the ecosystem of array-aware libraries,
sets documentation standards, provides array testing infrastructure,
and defines minimum version dependencies.

@@

Similar examples can be found in physics, earth science, biology,
and more.
Researchers in these fields depend on NumPy being correct, reliable,
and repeatable.
The rich ecosystem of tools building on NumPy and the larger community
of scientists and programmers using those tools mean that NumPy has a
responsibility to maintain considerable stability.
At times, this conflicts with the need to innovate;
resolving it requires balancing trade-offs.
% our focus is ...
% NumPy purpose engages with this problem by ...
% [this also defines the scope of NumPy]
This need creates interesting challenges for NumPy development as the
computational environment scientists are analyzing their data on continues
to evolve and change.
% this leads to a proliferation of arrays
